IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
s/SWAPI/COWL
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

In this section, we describe these two implementations.  Furthermore,
we consider how our formalism could be applied to the C programming
language, and connect it to a previous IFC system for Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different properties, as well as to discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the SWAPI~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the SWAPI implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

@@

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the worker JS object~\cite{webworkers}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across worker
  threads is undefined.
}
%
As suggested by our formal semantics, SWAPI can directly leverage these
mechanisms to implement the semantics of |specLangJS roundrobinf|
without modifying the JS runtime or intrusively changing the browser
layout engine.

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, SWAPI additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accommodating these
features lies outside the purview of our formalism.

%% \Red{
%% EZY:  This seems like useless detail about the SWAPI implementation
%% that is not relevant to this paper.
%% 
%% Of course, simply disallowing all external effects for all browsing
%% contexts would break most of the Web.
%% %
%% Hence SWAPI only enforces IFC, and thus restricts external effects,
%% when the JS code uses the new API.\footnote{
%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
%%   restricting external effects we interpose ``standard''
%%   \texttt{postMessage} communication to ensure that no information is
%%   leaked between contexts that have opted-in and those that have not.
%% }
%% %
%% Moreover, rather than disallowing all external effects, SWAPI allows
%% controlled network communication by leveraging the fact that web
%% pages already have an accompanying security policy: the same origin
%% policy.
%% %
%% Hence, for example, a worker that has read data only sensitive to
%% \texttt{http://bank.ch} can communicate with this domain; only once
%% \texttt{http://aws.com} data is also included in the context will all
%% network requests be blocked.
%% %
%% Of course, this requires that we use a concrete label format to
%% express the policies; we refer the interested reader to~\tocite{} for
%% more details.}

>>>>

In this section, we describe these two implementations.  Furthermore,
we consider how our formalism could be applied to the C programming
language, and connect it to a previous IFC system for Haskell.
%
Our goal is to show the flexibility of the embedding in settings with
vastly different properties, as well as to discuss the
semantic gap that must be overcome in some cases to apply our formalism
to other systems.
%
%% Two of the systems we describe have been implemented: the Haskell
%% system~\cite{lio} and the COWL~\cite{swapi} system; we leave the
%% implementation of the IFC system for C to future work.

@@

We remark that this is similar to the existing
\texttt{postMessage} API used for iframe and worker
communications~\cite{webworkers}.
%
Thus, the COWL implementation provides an IFC version of
\texttt{postMessage}, defined in terms of |send|, that additionally
takes a label argument.

@@

Unsurprisingly, our coarse-grained combined language approach has been
inspired by existing browser (security) architectures.
%
Browsers, for example, isolate pages of different origins by running
them in separate runtimes.
%
Similarly, they provide the worker JS object~\cite{webworkers}, which allows
JavaScript to execute code in separate threads with separate JS
runtimes (and fresh global objects).
%
In both cases, code relies on the \texttt{postMessage} message-passing
API for communication, similar to our system.\footnote{
  The message-passing approach is, in part, due to ECMAScript's lack
  of well-defined semantics for concurrency.
  %
  Hence sharing and accessing objects such as the DOM across worker
  threads is undefined.
}
%
As suggested by our formal semantics, COWL can directly leverage these
mechanisms to implement the semantics of |specLangJS roundrobinf|
without modifying the JS runtime or intrusively changing the browser
layout engine.

However, a simple implementation of just associating a label with
workers and browsing context (iframes and top-level pages) to enforce
IFC on the executing JavaScript is not sufficient, as APIs which
introduce extra computational effects must be manually made aware of information flow
control.
%
For example, the initial global object of a worker contains the
\texttt{XMLHttpRequest} (XHR) object, while the global object of a
browsing context additionally contains the DOM.
%
In both cases, JS code can trivially leak information (e.g., to the
network with XHR or persistent storage using the DOM).
%
To address this, COWL additionally uses content security policy (CSP) and
(iframe) sandboxes~\cite{csp1.1,html5} to restrict external effects according
to the label of a task (worker or browsing context).  Accommodating these
features lies outside the purview of our formalism.

%% \Red{
%% EZY:  This seems like useless detail about the COWL implementation
%% that is not relevant to this paper.
%% 
%% Of course, simply disallowing all external effects for all browsing
%% contexts would break most of the Web.
%% %
%% Hence COWL only enforces IFC, and thus restricts external effects,
%% when the JS code uses the new API.\footnote{
%%   Once a piece of code ``opts-in'' to use our IFC API, in addition to
%%   restricting external effects we interpose ``standard''
%%   \texttt{postMessage} communication to ensure that no information is
%%   leaked between contexts that have opted-in and those that have not.
%% }
%% %
%% Moreover, rather than disallowing all external effects, COWL allows
%% controlled network communication by leveraging the fact that web
%% pages already have an accompanying security policy: the same origin
%% policy.
%% %
%% Hence, for example, a worker that has read data only sensitive to
%% \texttt{http://bank.ch} can communicate with this domain; only once
%% \texttt{http://aws.com} data is also included in the context will all
%% network requests be blocked.
%% %
%% Of course, this requires that we use a concrete label format to
%% express the policies; we refer the interested reader to~\tocite{} for
%% more details.}
